---
title: "South African Lake Project"
author: "Simon Brewer"
date: "12/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Project aiming to simulate water balance for lakes in Nama Karoo region of South Africa

## Region

#### Nama Karoo region

This is the CRU 0.5 degree grid, currently used for climate data:

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
require(raster)
require(rgdal)
dem.r = raster("./cru/cl/bc_cru_10min_elv.nc") * 1000
bclake = readOGR("~/Documents/grassdata/hydrosheds/bclake/929m lake level.kml")
plot(dem.r)
plot(bclake, add=TRUE)
```

#### BC Lake

This is the 30 arc second grid, currently used for runoff simulation:

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
dem.r = raster("./dem/bclake_dem.nc")
plot(dem.r)
plot(bclake, add=TRUE)
```

This is the lake basin from GRASS GIS's `r.watershed` routine. Colored areas indicate the entire basin, green pixels are the lake's drainage watershed. 

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
bas.r = raster("./dem/bclake_bas.nc")
ws.r = raster("./dem/bclake_ws.nc")
x1 = !is.na(ws.r)
x2 = bas.r==19238
plot(x1+x2)
plot(bclake, add=TRUE)
```


## Notes and quotes

> "Evaporation and potential transpiration losses from vegetated surfaces and open water are everywhere high in Africa, evaporation from open water being on the order of 1500-2000 mm a year." Grove (1996). African River Discharges and Lake Levels in the 20th Century. In "Limnology, Climatology and Paleoclimatology of the East African Lakes", ed. Johnson and Odada. CRC Press